---
title: "SurvBregDiv: Transfer Learning for Time-to-Event Modelling via Bregman Divergence"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SurvBregDiv: Transfer Learning for Time-to-Event Modelling via Bregman Divergence}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  markdown:
    wrap: sentence
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.alt = "Plot generated in survkl vignette")
library(dplyr)
```


## Introduction

Accurate prognostic modeling is a central goal in survival analysis.
The rapid expansion of large-scale biobank initiatives—with rich genetic, molecular, imaging, and electronic health record data—has created new opportunities to improve predictive performance in clinical and epidemiologic research. However, these datasets often exhibit limited effective sample sizes, high dimensionality, low signal-to-noise ratios, and additional practical constraints including privacy considerations and restricted data access.

Integrating external information offers a principled strategy for improving model efficiency. Yet, classical data-integration methods typically rely on the assumption that multiple datasets arise from a common data-generating mechanism. In modern biomedical applications, this assumption is rarely satisfied. Misspecification due to population heterogeneity can induce substantial bias, motivating the development of transfer-learning approaches that explicitly accommodate between-source discrepancies.

While Bregman divergence has been successfully applied to borrowing information in binary-outcome settings, extending such ideas to censored time-to-event outcomes is nontrivial due to right censoring and the limited nature of available external survival information (e.g., predicted risk scores, fitted regression coefficients, or hazard ratios without access to a baseline hazard).

Beyond full-cohort survival studies, many biomedical investigations rely on the nested case–control (NCC) design to alleviate the burden of labor-intensive measurements, high-cost data acquisition, and destructive or finite biospecimen assays. Under an NCC design, only a small number of matched controls are sampled at each failure time, producing survival data that are analyzed through conditional logistic regression applied to matched risk sets. Despite its practical relevance, no existing methodology or software supports transfer learning or external information borrowing under NCC designs.

The `SurvBregDiv` package addresses these challenges by providing a unified transfer-learning framework for both full-cohort Cox data and nested case–control designs. The methods integrate external information in a privacy-preserving manner and are applicable to both low-dimensional settings and high-dimensional variable selection with ridge, lasso, and elastic net penalties.


### Key Features

- **Transfer learning via KL/Bregman shrinkage**  
  Integrates external information through Bregman divergence–based penalization, enabling adaptive borrowing from heterogeneous data sources.

- **Privacy-preserving external information use**  
  Operates on summary-level external inputs—such as fitted coefficients or risk scores—without requiring individual-level external data access.

- **Heterogeneity-aware borrowing**  
  Accommodates population differences through tuning-parameter–controlled shrinkage, selectively borrowing strength only when sources are compatible.

- **High-dimensional modeling with regularization**  
  Supports penalized KL-integrated models, including ridge, lasso, and elastic net penalties for variable selection and shrinkage.

- **Flexible external information formats**  
  Allows external inputs in the form of coefficients, risk scores, or partially overlapping covariate sets.

- **Built-in cross-validation for tuning**  
  Provides cross-validation criteria tailored for survival outcomes, including C-index, predicted deviance, and V&VH loss.

This vignette introduces the core functionalities of `SurvBregDiv` and illustrates workflows for both low- and high-dimensional applications.



## Installation

You can install from CRAN:

```{r, eval=FALSE}
install.packages("SurvBregDiv")
```

Or install the development version of `SurvBregDiv` from GitHub:

```{r, eval=FALSE}
require(devtools)
require(remotes)
remotes::install_github("UM-KevinHe/SurvBregDiv", ref = "main")
```


## Quick Start

This section provides a brief overview of the main functions using example datasets included in the package.

First, load the package:

```{r}
library(SurvBregDiv)
```

### Full-Cohort Cox Model with Bregman Divergence Integration


#### Low-Dimensional Integration

The low-dimensional Bregman-divergence–integrated Cox model is intended for settings where the number of predictors is modest. External information—either in the form of external Cox coefficients (`beta`) or pre-computed external risk scores (`RS`)—is incorporated through a Bregman-divergence penalization mechanism.

The tuning parameter `eta` controls the strength of information borrowing:

- `eta = 0` reduces to the standard Cox model (no external borrowing), and  
- larger values of `eta` increasingly shrink the fitted coefficients toward the external information.

Two specific divergence choices are supported:

- **Kullback–Leibler (KL) divergence**, implemented via `coxkl()`, and  
- **squared Mahalanobis distance**, implemented via `cox_MDTL()`.

For both formulations, the optimal `eta` can be selected through cross-validation using `cv.coxkl()` or `cv.cox_MDTL()`, respectively.


##### Low-dimensional Example Dataset:

We illustrate the workflow using the built-in low-dimensional simulated dataset `ExampleData_lowdim`, which consists of a training set (100 samples) and a test set (2000 samples) with 6 predictors. We first extract the training components:

```{r}
data(ExampleData_lowdim)

train  <- ExampleData_lowdim$train
test   <- ExampleData_lowdim$test

z      <- train$z
delta  <- train$status
time   <- train$time
strat  <- train$stratum
```

and externally derived coefficients beta_external:
```{r}
beta_ext <- ExampleData_lowdim$beta_external_fair
```

We generate a sequence of tuning parameter `eta` values via the internal utility `generate_eta()` and fit the integrated model across this grid:
```{r}
eta_list <- generate_eta(method = "exponential", n = 50, max_eta = 10)
```

##### Model Fitting:

For the KL divergence–based integrated model, we use the function `coxkl()`:

```{r}
coxkl_est <- coxkl(
  z = z,
  delta = delta,
  time = time,
  stratum = strat,
  beta = beta_ext,
  etas = eta_list
)
```

For the squared Mahalanobis distance–based integrated model, we use `cox_MDTL()`:

```{r}
cox_MDTL_est <- cox_MDTL(
  z = z,
  delta = delta,
  time = time,
  stratum = strat,
  beta = beta_ext,
  vcov = NULL,
  etas = eta_list
)
```

Note that the squared Mahalanobis distance formulation requires a user-specified weighting matrix \eqn{Q} via the argument `vcov`. In standard Mahalanobis distance settings, \eqn{Q} is taken to be the inverse covariance matrix of the coefficients. If `vcov = NULL`, the function defaults to the identity matrix.


Users may instead supply an external risk score vector:

```{r}
RS_ext <- as.matrix(z) %*% as.matrix(beta_ext)

coxkl_est.RS <- coxkl(
  z = z,
  delta = delta,
  time = time,
  stratum = strat,
  RS = RS_ext,
  etas = eta_list
)
```

For datasets containing tied event times, users may apply the `coxkl_ties()` function, which extends integrated Cox model to handle ties. The following example illustrates the use of the Breslow method for tie handling:


```{r}
time_ties <- round(time, 2)   # Rounding time introduces ties for demonstration

coxkl_ties_est <- coxkl_ties(
  z = z,
  delta = delta,
  time = time_ties,
  stratum = strat,
  beta = beta_ext,
  etas = eta_list,
  ties = "breslow"
)
```


##### Hyperparameter Tuning via Cross-Validation:

The function `cv.coxkl` and `cv.cox_MDTL` performs K-fold (default 5) cross-validation to choose the integration parameter.
It supports four criteria:

- `"V&VH"` — V&VH loss  
- `"LinPred"` — predicted partial deviance  
- `"CIndex_pooled"` — pooled comparable pairs  
- `"CIndex_foldaverage"` — per-fold stratified C-index  

Below is an example using the default `"V&VH"` criterion:

```{r}
cv.coxkl_est <- cv.coxkl(
  z = z,
  delta = delta,
  time = time,
  stratum = strat,
  beta = beta_ext,
  etas = eta_list,
  nfolds = 5,
  criteria = "V&VH",
  seed = 1)
```



##### Visualization:

Objects of model fittings (i.e. from either `coxkl` or `cox_MDTL`) from can be visualized using the S3 plotting method `plot()`.  
This function displays how model performance changes across the `eta`–sequence used during fitting.

Two types of performance criteria are supported:

- `"loss"`  
  (default; −2 × partial log-likelihood, normalized by sample size)

- `"CIndex"`  
  (stratified concordance index)
  
Users may directly call the `plot()` method to visualize the model's fitted performance on the training data without providing additional test data. If a test set is supplied, performance metrics are computed using the test set instead:

```{r}
plot(
  cox_MDTL_est,
  test_z       = test$z,
  test_time    = test$time,
  test_delta   = test$status,
  test_stratum = test$stratum,
  criteria     = "loss"
) 
```


The cross-validated performance curve from hyperparameter tuning functions `cv.coxkl` or `cv.cox_MDTL` can be visualized directly using `cv.plot()`:

```{r}
cv.plot(cv.coxkl_est)
```

- The solid purple curve displays the cross-validated loss across different values of `eta`.
- The green dotted horizontal line marks the internal baseline at `eta` = 0, representing the model that does not incorporate external information.
- The vertical dashed orange line indicates the optimal `eta` value, where the cross-validated loss is minimized.

A comparison between the purple curve and the green baseline shows whether borrowing external information improves prediction performance.
Whenever the purple curve falls below the green line, using external information (`eta` > 0) yields better predictive accuracy than relying solely on the internal model.



#### High-Dimensional Integration

In high-dimensional regimes—such as when the number of predictors is comparable to or exceeds the sample size—the `SurvBregDiv` package extends Bregman-divergence–integrated Cox modeling with regularization. Similar to the low-dimensional setting, both **Kullback–Leibler (KL) divergence** and **squared Mahalanobis distance** are supported as specific Bregman choices for external information integration.

Two families of penalties are implemented:

- **Ridge penalty (L2)**, via `coxkl_ridge` and `cox_MDTL_ridge`, which shrinks coefficients toward zero while yielding dense solutions.
- **Elastic net penalty (mix of L1 and L2)**, via `coxkl_enet` and `cox_MDTL_enet`, where the **LASSO** corresponds to the special case with mixing parameter set to 1.

These models combine:

- an **integration penalty**, controlled by `eta`, to borrow information from external sources (risk scores `RS` or coefficients `beta`), and  
- a **regularization penalty** (ridge or elastic net) to stabilize estimation under high-dimensional designs.

In what follows, we introduce the shared high-dimensional example dataset and demonstrate the usage of the penalized KL divergence model. 

*Note: The squared Mahalanobis distance counterparts follow an identical workflow.*


##### High-dimensional Example Dataset:

The built-in high-dimensional simulated dataset `ExampleData_highdim` contains a training set (200 samples) and a test set (2000 samples). The dataset includes 50 predictors (`Z1`–`Z50`), of which 6 are signal variables and the remaining 44 are AR(1) noise variables. Externally derived coefficients are provided in `beta_external`:


```{r}
data(ExampleData_highdim)

train_hd  <- ExampleData_highdim$train
test_hd   <- ExampleData_highdim$test

z_hd      <- train_hd$z
delta_hd  <- train_hd$status
time_hd   <- train_hd$time
strat_hd  <- train_hd$stratum

beta_external_hd <- ExampleData_highdim$beta_external
```


##### Model Fitting:

###### Ridge-Penalized Integrated Cox Model

The function `coxkl_ridge()` fits a KL-integrated Cox model with a ridge (L2) penalty on all predictors. External information is incorporated through a KL-based integration term weighted by `eta` (a user-specified scalar), while regularization is imposed through a sequence of tuning parameters `lambda`. If `lambda` is not provided, the function automatically generates a decreasing lambda path.

We begin by fitting a KL–ridge model for a fixed integration weight `eta` using an automatically generated lambda sequence:

```{r}
model_ridge <- coxkl_ridge(
  z        = z_hd,
  delta    = delta_hd,
  time     = time_hd,
  stratum  = strat_hd,
  beta     = beta_external_hd,
  eta      = 1                 
)
```
The fitted object stores, for each value of `lambda`:

- `model_ridge$lambda` — the sequence of lambda values (in decreasing order),
- `model_ridge$beta` — estimated coefficients (one column per lambda),
- `model_ridge$linear.predictors` — linear predictors for all observations across the lambda path,
- `model_ridge$likelihood` — partial log-likelihood along the lambda path,
- `model_ridge$data` — the data used for fitting.


###### Elastic-Net / LASSO-Penalized Integrated Cox Model

The function `coxkl_enet()` fits a KL-integrated Cox model with an elastic-net penalty, controlled by the mixing parameter `alpha`. When `alpha = 1`, the penalty reduces to *LASSO*, introducing coefficient sparsity in addition to KL-based integration of external information.

External knowledge can be incorporated either through external coefficients (`beta`) or through an externally computed risk score (`RS`). The integration parameter `eta` determines how strongly the model borrows from this external information, while the penalty parameter `lambda` controls sparsity. If `lambda` is not provided, the function automatically generates a decreasing lambda sequence.

Below, we illustrate the workflow using the *LASSO* special case (`alpha = 1`) with an automatically generated lambda path:

```{r}
model_enet <- coxkl_enet(
  z        = z_hd,
  delta    = delta_hd,
  time     = time_hd,
  stratum  = strat_hd,
  beta     = beta_external_hd,   
  eta      = 1,                 
  alpha    = 1                  # LASSO penalty
)
```

The fitted object stores, for each lambda value:

- `model_enet$lambda` — the lambda sequence (in decreasing order),
- `model_enet$beta` — estimated coefficients (one column per lambda),
- `model_enet$likelihood` — partial log-likelihood along the lambda path,
- `model_enet$data` — the data used for fitting.



##### Hyperparameter Tuning via Cross-Validation

For penalized integrated models, the functions `cv.coxkl_ridge()` and `cv.coxkl_enet()` perform K-fold cross-validation to tune the integration parameter `eta`, while internally scanning over a `lambda` path for each candidate `eta`. For each value of `eta`, the cross-validation procedure:

- evaluates a sequence of ridge or elastic-net penalties `lambda`,
- computes the chosen cross-validation criterion on the held-out folds,
- selects the best `lambda` for that `eta`,
- aggregates the performance across folds into summary tables.

The following criteria are supported:

- `"V&VH"` — V&VH loss (reported as `Loss = -2 * score`),
- `"LinPred"` — predicted partial deviance,
- `"CIndex_pooled"` — pooled C-index across all folds,
- `"CIndex_foldaverage"` — fold-averaged C-index.

Below we demonstrate tuning `eta` using 5-fold cross-validation and the `"V&VH"` criterion for the LASSO-penalized integrated model (`alpha = 1`). (For ridge, use `cv.coxkl_ridge()` analogously.)


```{r}
eta_grid_hd <- generate_eta(method = "exponential",
                            n = 50,
                            max_eta = 100)

cv_enet_hd <- cv.coxkl_enet(
  z = z_hd,
  delta = delta_hd,
  time = time_hd,
  stratum = strat_hd,
  beta = beta_external_hd,
  etas = eta_grid_hd,
  alpha = 1, # LASSO
  nfolds = 5,
  cv.criteria = "V&VH",
  seed = 1
)
```


The best `lambda` for each `eta` (according to the chosen criterion) is provided by:

```{r}
cv_enet_hd$integrated_stat.best_per_eta
```

##### Visualization:

Objects from `coxkl_ridge` or `coxkl_enet` can be visualized using the S3 plotting method `plot()`:

This plots (at given `eta`):

- Loss or C-index versus the penalty parameter `lambda`,
- x-axis on a reversed log10 scale (larger penalties on the left, smaller penalties on the right),
- y-axis labeled as loss or C-index,.
- A vertical dashed orange line marks the optimal value of λ, where the loss reaches its minimum on the evaluated grid.


```{r}
plot(
  model_enet,
  test_z       = test_hd$z,
  test_time    = test_hd$time,
  test_delta   = test_hd$status,
  test_stratum = test_hd$stratum,
  criteria     = "loss"
)
```


As with low-dimensional models, the helper function `cv.plot()` can be used to visualize performance versus `eta`:

```{r}
cv.plot(cv_enet_hd)
```
The resulting plot displays:

- a purple curve showing the cross-validated performance across the `eta` sequence (loss or C-index),
- a green dotted horizontal line indicating the internal baseline at `eta = 0`,
- a green point marking the baseline performance,
- and a vertical dashed orange line denoting the optimal `eta`, where the cross-validated loss attains its minimum.


##### Stability Selection for High-Dimensional Models

Classical LASSO tuned via cross-validation performs well for prediction, but it is often unstable for variable selection: small perturbations of the data or changes in cross-validation splits may lead to different selected subsets, particularly in high-dimensional or correlated settings. Stability selection provides a complementary approach that emphasizes reproducibility by repeatedly perturbing the data and recording how frequently each variable is selected across subsamples.

The functions `coxkl_enet.StabSelect()` and `cox_MDTL_enet.StabSelect()` extend the cross-validated elastic-net procedures (`cv.coxkl_enet()` and `cv.cox_MDTL_enet()`) by repeatedly fitting the integrated elastic-net model on multiple subsamples (controlled by the parameter `B`). For each subsample, the model is fit using its own cross-validated tuning parameters, and the selection status of each variable along the regularization path is recorded. The function returns the empirical selection frequency of each variable across resamples and across the entire penalty path, providing a stability-oriented summary of variable importance.


```{r}
coxkl.StabSelect <- coxkl_enet.StabSelect(
  z = z_hd,
  delta = delta_hd,
  time = time_hd,
  stratum = strat_hd,
  beta = beta_external_hd,
  etas = eta_list,
  cv.criteria = "CIndex_pooled",
  B = 20
)
```

`ox_MDTL_enet.StabSelect` follows an identical workflow. Objects from `coxkkl_enet.StabSelect or `ccox_MDTL_enet.StabSelect can be visualized using the S3 plotting method `plot()`:, 用户需要指定 a selection frequency threshold (between 0 and 1). Variables whose selection frequency exceeds this threshold are highlighted in the plot, while others are shown in a muted color. The x-axis represents the penalty parameter `lambda` on a reversed log10 scale, and the y-axis shows the selection frequency:

```{r}
plot(coxkl.StabSelect, threshold = 0.6) 
```

##### Bagging for High-Dimensional Models

Besides cross-validated LASSO and stability selection, we additionally support an ensemble strategy that combines bootstrapping, external-data integration, and model aggregation. Conceptually similar to bootstrap aggregation (bagging).

For each bootstrap sample, the integrated model is refit with its own cross-validated tuning parameters, and the resulting linear predictors are aggregated across bootstrap replicates. Unlike stability selection, the goal here is not variable selection, but prediction stabilization: different bootstrap replicates may recruit different levels of external borrowing, allowing weak or noisy external signals to be averaged out rather than over-amplified by a single fit. As a result, this bagged integration approach reduces variance and improves predictive robustness compared to relying solely on a single cross-validated integrated LASSO model.


The functions `coxkl_enet_bagging()` and `cox_MDTL_enet_bagging()` implement this ensemble strategy. The following example demonstrates how to apply `coxkl_enet_bagging()` for bagged integration in high-dimensional settings. The function inherits the arguments of `cv.coxkl_enet()`, with an additional parameter `B` that controls the number of subsamples used in the ensemble.


```{r, eval=FALSE, message=FALSE}
bagging.coxkl <- coxkl_enet_bagging(
  z = z_hd,
  delta = delta_hd,
  time = time_hd,
  stratum = strat_hd,
  beta = beta_external_hd,
  etas = eta_list,
  B = 5,
  seed = 1
)
```

The returned object contains the bagged coefficient estimate (stored in `bagging.coxkl$best_beta`) as well as the all bootstrap-specific estimates (`bagging.coxkl$all_betas`). In practice, `bagging.coxkl$best_beta` can be treated as the final integrated elastic-net coefficient vector for downstream analysis; for example, risk scores on a new design matrix `z_new` can be computed via the linear predictor `z_new %*% bagging.coxkl$best_beta`, while `bagging.coxkl$all_betas` can be inspected to assess the variability of the bootstrap ensemble.



### Nested Case-Control (NCC) Design with Bregman Divergence Integration

In the NCC setting, event times are represented through matched case–control sets and estimation proceeds via conditional logistic regression. `SurvBregDiv` enables external information borrowing within this framework through Bregman divergence, allowing improved efficiency while respecting the matched-set structure. The remainder of this section demonstrates the core usage and workflow.


#### Low-Dimensional Integration

##### Example Dataset:

The built-in simulated dataset for NCC designs, `ExampleData_cc`, contains a training set (1000 samples) and a test set (2500 samples). The data include a `stratum` variable, where observations with the same stratum ID belong to the same matched set. The training data contain 200 matched sets and the test data contain 500 matched sets, each constructed under a 1:4 matching scheme. The dataset further includes six predictors (`Z1`–`Z6`). Externally derived coefficients are provided in `beta_external`:

```{r}
data(ExampleData_cc)

train.cc  <- ExampleData_cc$train
test.cc   <- ExampleData_cc$test

z.cc      <- train.cc$z
y.cc      <- train.cc$y
set.cc    <- train.cc$stratum

beta_ext.cc <- ExampleData_cc$beta_external
```


##### Model Fitting and Hyperparameter Tuning

The main fitting function for this setting is `clogitkl`. Users must specify the tie-handling method via the `method` argument. For 1:M matched case–control studies, `"breslow"` and `"exact"` yield identical results, although `"exact"` is theoretically preferable. For n:m matched designs with \(n > 1\), the two methods can differ.


```{r}
eta_list <- generate_eta(method = "exponential", n = 50, max_eta = 5)

clogitkl.fit_breslow <- clogitkl(y = y.cc, z = z.cc, stratum = set.cc, 
                                 eta = eta_list, beta = beta_ext.cc,
                                 method = "breslow")
```


The object returned by `clogitkl` can be visualized using the S3 `plot()` method. Its usage is consistent with the full-cohort integrated Cox model introduced earlier:

```{r}
plot(
  clogitkl.fit_breslow,
  test_z       = test.cc$z,
  test_delta   = test.cc$y,
  test_stratum = test.cc$stratum,
  criteria     = "loss"
)
```

Similarly, cross-validation for tuning `eta` can be performed via `cv.clogitkl()`, which shares the same interface and functionality as its full-cohort counterparts:

```{r}
cv.clogitkl.fit_breslow <- cv.clogitkl(
  y        = y.cc,
  z        = z.cc,
  stratum  = set.cc,
  beta     = beta_ext.cc,
  etas     = eta_list,
  method   = "exact",
  nfolds   = 5,
  criteria = "loss"
)
```


The cross-validated performance curve can be visualized using `cv.plot()`:

```{r}
cv.plot(cv.clogitkl.fit_breslow)
```
As before, the plot displays a purple curve tracing the cross-validated performance across the `eta` grid, a green dotted horizontal line representing the internal baseline at `eta = 0` (with a green point marking its value), and a vertical dashed orange line indicating the optimal `eta` at which the cross-validated loss is minimized.


#### High-Dimensional Integration


##### Example Dataset:

The built-in simulated dataset for NCC designs, `ExampleData_cc_highdim`, contains a training set with 50 matched sets and a test set with 500 matched sets, each constructed under a 1:5 matching scheme. The dataset includes 10 predictors (`Z1`–`Z20`). Externally derived coefficients are provided in `beta_external`:

```{r}
data(ExampleData_cc_highdim)

train.cc_hd  <- ExampleData_cc_highdim$train
test.cc_hd   <- ExampleData_cc_highdim$test

z.cc_hd      <- train.cc_hd$z
y.cc_hd      <- train.cc_hd$y
set.cc_hd    <- train.cc_hd$stratum

beta_ext.cc_hd <- ExampleData_cc_highdim$beta_external
```


##### Model Fitting and Hyperparameter Tuning

For high-dimensional NCC data, we demonstrate usage with `clogitkl_enet()`, which fits KL-integrated conditional logistic regression models with elastic-net penalties. The interface and workflow are analogous to those for the full-cohort integrated Cox functions.


```{r}
clogitkl_enet_fit <- clogitkl_enet(
  y       = y.cc_hd,
  z       = z.cc_hd,
  stratum = set.cc_hd,
  beta    = beta_ext.cc_hd,
  eta     = 0
)
```

The fitted object can be visualized using the S3 `plot()` method:

```{r}
plot(
  clogitkl_enet_fit,
  test_z       = test.cc_hd$z,
  test_delta   = test.cc_hd$y,
  test_stratum = test.cc_hd$stratum,
  criteria     = "loss"
)
```

Cross-validation for tuning `eta` can be performed via `cv.clogitkl_enet()`:

```{r}
eta_list <- generate_eta(method = "exponential", n = 50, max_eta = 5)

cv.clogitkl_enet_fit <- cv.clogitkl_enet(
  y        = y.cc_hd,
  z        = z.cc_hd,
  stratum  = set.cc_hd,
  beta     = beta_ext.cc_hd,
  etas     = eta_list,
  alpha    = 1,
  nfolds   = 5,
  criteria = "loss"
)

```
The cross-validated performance curve can be visualized using `cv.plot()`:

```{r}
cv.plot(cv.clogitkl_enet_fit)
```

As before, the plot displays a purple curve tracing the cross-validated performance across the `eta` grid, a green dotted horizontal line representing the internal baseline at `eta = 0` (with a green point marking its value), and a vertical dashed orange line indicating the optimal `eta` at which the cross-validated loss is minimized.
