---
title: "SurvBregDiv: Transfer Learning for Time-to-Event Modelling via Bregman Divergence"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{survkl: Transfer-Learning Based Integrated Cox Models}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  markdown:
    wrap: sentence
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.alt = "Plot generated in survkl vignette")
library(SurvBregDiv)

library(dplyr)
library(kableExtra)
```


## Introduction

Accurate prognostic modeling is a central goal in survival analysis.
The rapid expansion of large-scale biobank initiatives—with rich genetic, molecular, imaging, and electronic health record data—has created new opportunities to improve predictive performance in clinical and epidemiologic research. However, these datasets often exhibit limited effective sample sizes, high dimensionality, low signal-to-noise ratios, and additional practical constraints including privacy considerations and restricted data access.

Integrating external information offers a principled strategy for improving model efficiency. Yet, classical data-integration methods typically rely on the assumption that multiple datasets arise from a common data-generating mechanism. In modern biomedical applications, this assumption is rarely satisfied. Misspecification due to population heterogeneity can induce substantial bias, motivating the development of transfer-learning approaches that explicitly accommodate between-source discrepancies.

While Bregman divergence has been successfully applied to borrowing information in binary-outcome settings, extending such ideas to censored time-to-event outcomes is nontrivial due to right censoring and the limited nature of available external survival information (e.g., predicted risk scores, fitted regression coefficients, or hazard ratios without access to a baseline hazard).

Beyond full-cohort survival studies, many biomedical investigations rely on the nested case–control (NCC) design to alleviate the burden of labor-intensive measurements, high-cost data acquisition, and destructive or finite biospecimen assays. Under an NCC design, only a small number of matched controls are sampled at each failure time, producing survival data that are analyzed through conditional logistic regression applied to matched risk sets. Despite its practical relevance, no existing methodology or software supports transfer learning or external information borrowing under NCC designs.

The `SurvBregDiv` package addresses these challenges by providing a unified transfer-learning framework for both full-cohort Cox data and nested case–control designs. The methods integrate external information in a privacy-preserving manner and are applicable to both low-dimensional settings and high-dimensional variable selection with ridge, lasso, and elastic net penalties.


### Key Features

- **Transfer learning via KL/Bregman shrinkage**  
  Integrates external information through Bregman divergence–based penalization, enabling adaptive borrowing from heterogeneous data sources.

- **Privacy-preserving external information use**  
  Operates on summary-level external inputs—such as fitted coefficients or risk scores—without requiring individual-level external data access.

- **Heterogeneity-aware borrowing**  
  Accommodates population differences through tuning-parameter–controlled shrinkage, selectively borrowing strength only when sources are compatible.

- **High-dimensional modeling with regularization**  
  Supports penalized KL-integrated models, including ridge, lasso, and elastic net penalties for variable selection and shrinkage.

- **Flexible external information formats**  
  Allows external inputs in the form of coefficients, risk scores, or partially overlapping covariate sets.

- **Built-in cross-validation for tuning**  
  Provides cross-validation criteria tailored for survival outcomes, including C-index, predicted deviance, and V&VH loss.

This vignette introduces the core functionalities of `SurvBregDiv` and illustrates workflows for both low- and high-dimensional applications.



## Installation

You can install from CRAN:

```{r, eval=FALSE}
install.packages("SurvBregDiv")
```

Or install the development version of `SurvBregDiv` from GitHub:

```{r, eval=FALSE}
require(devtools)
require(remotes)
remotes::install_github("UM-KevinHe/SurvBregDiv", ref = "main")
```










